Categorical Predictor Embeddings in Actuarial Modeling

### 2021-03-10 manuscript/manuscript.Rmd

For Model 2, we build a feedforward neural network. The categorical inputs go through one-dimensional embedding
layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
have been normalized in data pre-processing, before being sent to a single linear layer of 16 units. A ReLU activation
is then applied to the outputs before they are sent to a final linear layer resulting in a scalar. To constrain
predictions to be positive, we apply softplus activation, which is defined to be

@@

```{r nn-1, echo = FALSE, fig.cap = "blahblah", out.width = "90%", fig.align = "center"}
knitr::include_graphics("images/nn.png")
```

@@

@@

## Performance evaluation framework and results

>>>>

For Model 2, we build a feedforward neural network. The categorical inputs go through one-dimensional embedding
layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
have been normalized in data pre-processing, before being sent to a hidden linear layer of 16 units. A ReLU (TODO: reference an equation in prev. section) activation
is then applied to the outputs before they are sent to a final output layer resulting in a scalar. To constrain
predictions to be positive, we apply softplus activation, which is defined to be

@@

```{r nn-1, echo = FALSE, fig.cap = "Architecture of Models 2 and 4.", out.width = "90%", fig.align = "center"}
knitr::include_graphics("images/nn.png")
```

With a single hidden layer, this architecture is the simplest nontrivial neural network; without the hidden layer and
corresponding ReLU activation, we would actually recover a GLM structure where the link function is the output activation. 
The choice of one for the embedding dimension is also due to simplicity: it is easily interpretable as the representation
of each factor level as a point on the real number line, also, the trained embeddings are easily incorporated into a GLM
which we will see in Model 3. In practice, the embedding dimension is a hyperparameter one can tune, for example via
cross validation, and can vary for each variable. However, we also note that the choice of one for the 
embedding output dimension is not an unreasonable one, especially when the cardinalities of the categorical variables
are not unusually large.

@@

For Model 3, we return to the GLM, but now we replace the categorical variables with the trained embeddings from Model
2. In other words, our model now contains only continuous variables, and each categorical factor is represented as a
scalar value and obtains its own coefficient. (TODO: insert formal eqn for mean)

@@

## Model Training and Results
